Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-05 edubots_surveys.Rnw
Second Paragraph in Introduction
Updated the second paragraph in the introduction

% TODO: introduction
The introduction of new technologies in the classroom involves a combination of teacher training, student enthusiasm and possibly acquiring new skills by both. Some technologies are readily adapted, but others require longer time for full adoption. In most cases, the magnitude of the uptake of the new technology impinges on the collaboration of all the parties using it. Hence, examining the users’ attitudes and the opinions is an important first step in boosting this collaboration and reaping the benefits of the technology.  Recently, a surge in the use of synchronous instant messaging tools in higher education such as WhatsApp, Telegram and Facebook Messenger took place. Some messaging applications have built in chatbots that are able to support a synchronous conversation between the different parties \cite{differ.chat}, while other chatbots are developed as standalone systems and can possibly be attached to a messaging application using an API (Application Program Interface). 
The introduction of new technologies in the classroom needs a combination of teacher motivation, 
student willingness and (possibly new) skills in both. Some technologies are readily adapted, but some of them take a long time to be adopted. In most cases, the success or failure of the introduction of a new technology impinges on the collaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.

In the framework of the EduBots KA2 European project\footnote{https://www.edubots.eu}, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms. A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker's question fluently, and even ask other questions to the human. However, in most cases a simple messaging-application attached bot will help the students (and teachers); so neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications (e.g. Telegram, WhatsApp) used nowadays.
% Antonio - This paragraph needs a conclusion. Why do we say (essentially) that chatbots are not needed and just a simple messaging bot is enough?
% JJ - feel free to add one 
% Antonio - The thing is I don't catch why are we saying that, since it is supossed that we should 'defend' the use of chatbots (from the project perspective, at least). Or if we don't want to defend them, at least not saying that they are useless most of times. XD
% Moreover, considering that in the following paragraphs we are trying to 'sell' them.

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
adapting individuals' pace of learning, who get customized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.

>>>>

% TODO: introduction
The introduction of new technologies in the classroom needs a combination of teacher motivation, 
student willingness and (possibly new) skills in both. Some technologies are readily adapted, but some of them take a long time to be adopted. In most cases, the success or failure of the introduction of a new technology impinges on the collaboration of all the implied parties, which is why evaluating attitudes towards them is an essential first step.

In the framework of the EduBots KA2 European project\footnote{https://www.edubots.eu}, we are mainly concerned with the creation of best practices in the use of chatbots in higher education classrooms. A \textit{chatbot} is a program, sometimes based on Artificial Intelligence techniques, that allows a computer to communicate in a similar way as a human does \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{moor2003turing}, since they are able to answer almost any speaker's question fluently, and even ask other questions to the human. However, in most cases a simple messaging-application attached bot will help the students (and teachers); so neither computational intelligence nor comprehension of natural languages are requisites, the only one being the fact that they can be accessed from a synchronous conversational application such as the common instant messaging applications (e.g. Telegram, WhatsApp) used nowadays.
% Antonio - This paragraph needs a conclusion. Why do we say (essentially) that chatbots are not needed and just a simple messaging bot is enough?
% JJ - feel free to add one 
% Antonio - The thing is I don't catch why are we saying that, since it is supossed that we should 'defend' the use of chatbots (from the project perspective, at least). Or if we don't want to defend them, at least not saying that they are useless most of times. XD
% Moreover, considering that in the following paragraphs we are trying to 'sell' them.
A chatbot is a program, sometimes developed using Artificial Intelligence techniques, that allows a computer to communicate in a similar way as humans do \cite{Gong2008}, using natural language. Indeed, most of them would be, apparently, close to passing a classic Turing test \cite{ moor2003turing }, since they are able to answer almost any question fluently, and even pose questions in their conversations. The recent advancement in this discipline has played an important role in many fields especially in education and online tutoring \cite{clarizia2018,Smutny2020}. These automatic systems facilitate the delivery of personalized learning by adapting to students’ pace of learning and providing customized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experiences as well as improving individual attention \cite{agarwal2020}.
The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
adapting individuals' pace of learning, who get customized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
